%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
	
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\Large\bf Kevin Weng} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline {145 N Idaho St. San Mateo, CA, 94401} 
\moveleft.5\hoffset\centerline {\href{mailto:kevinweng@g.ucla.edu}{kevinweng@g.ucla.edu} | \href{https://kevweng.github.io/} {650.808.7678}}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\large EDUCATION}

{\bf University of California, Los Angeles (UCLA)} \hfill{\sl c.o. 2022}\\
{\sl}{\bf  BS. Mathematics, B.S. Statistics; Specialization in Computing}\\ ACT: 35 | SAT Math II: 800\\
{\bf Coursework:} Probability Theory, Stochastic Processes, Linear Algebra (Honors), Enumerative Combinatorics, Optimization, Machine Learning, Complex Analysis, Algorithms\\
{\bf Activities:} ACM Artificial Intelligence
%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\large SKILLS} 

{\bf Programming Languages:} 
Python, R, C++\\ 
{\bf Technologies:}
Pandas, Git, Vim, NumPy,  Jupyter, Excel, {\LaTeX}, Linux/UNIX
%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section{\large EXPERIENCE}

{\sl {\bf Biostatistics Intern @ \href {https://goodarzilab.ucsf.edu/}{Goodarzi Lab (UCSF)}} \hfill May 2017 - Feb 2018} \\
San Francisco, CA

\begin{itemize} \itemsep -1pt % Reduce space between items
\item Implemented analysis of ribosome profiling datasets into an R framework at the Goodarzi Lab under Hani Goodarzi, Ph.D. 
\item Programmed a package in R using logistic regression and normalization to ribosome sequencing data.
\item Created a predictive model for metastatic and non-metastatic breast cancer cell lines.
\end{itemize}
 
{\sl {\bf President, Millbrae Branch} \hfill Sep 2016 - Jun 2018} \\
Burlingame, CA
\begin{itemize}  \itemsep -1pt
\item Synthesized research papers into informational articles for our website. 
\item Taught students topics including the immune system and immunotherapies.
\item Partnered with professors and doctors at Stanford and UCSF to expand research opportunities.
\end{itemize} 

%----------------------------------------------------------------------------------------


%---------------------------------------------------------------------------------------- 

\section{\large PROJECTS} 
{\sl {\bf Global Video Game Sales Predictor} \hfill Jun 2020 - Current} \\
San Mateo, CA
\begin{itemize}  \itemsep -1pt
\item Developing a model to predict global video game sales through local sales data and meta-game data. 
\item Exploring the efficacy of regression models including linear regression, Random Forest, and K-Nearest Neighbors.
\end{itemize} 

{\sl {\bf Quantitative Research} \hfill Jun 2019 - Current} \\
San Mateo, CA
\begin{itemize}  \itemsep -1pt
\item Developing a backtester for different algorithmic trading strategies using Python.
\item Testing mean reversal and momentum strategies on historical data.
\item Working on an event driven automated execution trading system. 
\end{itemize} 

%----------------------------------------------------------------------------------------
\section{\large INTERESTS}
Quantitative Research, Deep Learning, Trading, Civilization, Coffee, Fitness, Piano

%----------------------------------------------------------------------------------------
\section{\large LINKS}

\href{https://www.linkedin.com/in/kevweng/}{linkedin.com/in/kevweng}\\
\href{https://github.com/kevweng}{github.com/kevweng}\\
\href{https://kevweng.github.io}{kevweng.github.io}
\end{resume}
\end{document}